quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Need to find a way to remove the padding

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr;",
                   scurve_umap_plt_int, hex_grid_poly_scurve_int,
                   hex_centroids_scurve_int, wireframe_scurve_int,
                    htmltools::div(
                      style = "margin-top: 13px;",  # adjust px as needed
                      scurve_umap_model_vis_n
                    )),
    device = "xs"
  )
```

>>>>

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr 1fr 1fr 1fr; gap: 0;",
    htmltools::div(style = "margin: 0; padding: 0;", scurve_umap_plt_int),
    htmltools::div(style = "margin: 0; padding: 0;", hex_grid_poly_scurve_int),
    htmltools::div(style = "margin: 0; padding: 0;", hex_centroids_scurve_int),
    htmltools::div(style = "margin: 0; padding: 0;", wireframe_scurve_int),
    htmltools::div(
      style = "margin-top: 13px;",
      scurve_umap_model_vis_n
    )),
    device = "xs"
  )
```
